Title
========================================================

Let's see if we can install our nascent package on Unix
```{r}
install.packages("TeachingPopGen",repos=NULL,type="source")
```

OK.  All the depends need to be installed.  And for Unix, it is important to install the public key and do sudo apt-get update and sudo apt-get upgrade.  I'm wondering if there is a way this can be automated in the install.packages 
```{r}

```

Trying a compiled c load per [this](http://users.stat.umn.edu/~geyer/rc/)
```{r}
dyn.load("foo.so")
```
Had to move it into the working directory, but it's a start.  What we'll do is to write a function to call it, stick it in the package, and see if it will fly like that.  But let's try a call first
```{r}
x = .C("foo",n=5, x=as.double(seq(.2,1,.2)))
x
```
OK.  It works, but it's rather awkward.  Try a wrapper function
```{r}
foof <- function(x) {
           if (!is.numeric(x))
                   stop("argument x must be numeric")
           out <- .C("foo",
                   n=as.integer(length(x)),
                   x=as.double(x))
           return(out$x)
   }
```
OK.  That works.  Now to put it into a file and add it to the package.  